Epsilonciv has changed its implementation design more than one time. 

Initially the TDD-process let us to the thoughts: \\
Where to store the information about the number of battles won of each player?

We had already refactored out just what the game does to decide the winner of a game, into its own method and delegated it into a new strategy, at this point.\\

The first edition stored the data on the Enum Player, so that any interface with access to Framework.Player could actually access the information, but unfortunately also change it.

The second edition stored the state-information in game, and only allowed gameImpl to change it.

The third and current edition moved the responsibility of accessing the information and incrementing the player specific counters into a new interface, BattlesWatcher\footnote{BattlesWatcher is subject to change.} 
and let the epsilon implementation of the interfaces WinStrategy\footnote{WinStrategy is the interface with responsibility of determining the current game winner and is accesed through Game.getWinner()}
 and BattleStrategy\footnote{BattleStrategy is the interface with responsibility of determining between 2 tiles with units and the state of the game which unit that is the winner of a possible battle. This is used in Game.moveUnit(), in the case that a unit moves on top of an enemy unit.}
 be handled by the same object that, consequently, took care of the responsibility of BattlesWatcher.
\\

As such the design for epsilon was not fully fledged until very late in the TDD process and still the BattleStrategy is not fully implemented for the epsilon variant.

EpsilonBestOf5BattlesWinStrategy\footnote{The Epsilon specific strategy that both handles the responsibility of WinStrategy and BattleStrategy.} is therefore an item on our backlog\footnote{See \nameref{backlog}}.
